---
title: "Willow Creek Dashboard"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    theme: "cosmo"
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(gganimate)
library(plotly)
library(tidyverse)
library(rpart)
library(rattle)
#source("/fs/data3/kzarada/NEFI/Willow_Creek/animated_WCr_graphs.R")
#source("/fs/data3/kzarada/pecan/modules/assim.sequential/inst/WillowCreek/download_WCr_met.R")
load("/srv/shiny-server/Willow_Creek/data/wcr.RData")

```

Forecast
=======================================================================

### NEE
```{r}
 ggplot.nee<-ggplotly(p, tooltip = c("Time", "y", "Lower", "Upper")) %>% 
    animation_opts(frame = 1200, easing = 'linear-in', transition = 0, redraw = F, mode = "next") %>% 
    animation_slider(x = 0, y = -0.1, visible = T, currentvalue = list(prefix = "Forecast Date:", font = list(color = 'black'))) %>%
    animation_button(x = 0, xanchor = "left", y = 1.5, yanchor= "top") %>% 
    layout(legend = list(orientation = "h", x = 0.25, y = 1.1)) %>% 
    layout(showlegend = T, margin = c(30,50,30,50)) 
  
  ggplot.nee$x$data[[1]]$name <-"95% Confidence Interval"
  ggplot.nee$x$data[[2]]$name <- "Observed Data"
  ggplot.nee$x$data[[3]]$name <- "Predicted Mean"
  
  ggplot.nee
```

### LE
```{r}
  ggplot.le <- ggplotly(q, tooltip = c("Time", "y", "Lower", "Upper")) %>% 
    animation_opts(frame = 1200, easing = 'linear-in', transition = 0, redraw = F, mode = "next") %>% 
    animation_slider(x = 0, y = -0.1, visible = T, currentvalue = list(prefix = "Forecast Date:", font = list(color = 'black'))) %>%
    animation_button(x = 0, xanchor = "left", y = 1.5, yanchor= "top") %>% 
    layout(legend = list(orientation = "h", x = 0.25, y = 1.1)) %>% 
    layout(showlegend = T, margin = c(30,50,30,50)) 
  
  ggplot.le$x$data[[1]]$name <-"95% Confidence Interval"
  ggplot.le$x$data[[2]]$name <- "Observed Data"
  ggplot.le$x$data[[3]]$name <- "Predicted Mean"
  
  ggplot.le
```

###Soil Moisture Fraction
```{r}
ggplot.soil<-ggplotly(s, tooltip = 'all', layerData = 2) %>% 
    animation_opts(frame = 1200, easing = 'linear-in', transition = 0, redraw = F, mode = "next") %>% 
    animation_slider(x = 0, y = -0.1, visible = T, currentvalue = list(prefix = "Forecast Date:", font = list(color = 'black'))) %>%
    animation_button(x = 0, xanchor = "left", y = 1.5, yanchor= "top") %>% 
    layout(legend = list(orientation = "h", x = 0.25, y = 1.1)) %>% 
    layout(showlegend = T, margin = c(30,50,30,50)) 
  
  ggplot.soil$x$data[[1]]$name <-"95% Confidence Interval"
  ggplot.soil$x$data[[2]]$name <- "Observed Data"
  ggplot.soil$x$data[[3]]$name <- "Predicted Mean"
  
ggplot.soil
```

###PhenoCam

See the Willow Creek site live [here](https://phenocam.sr.unh.edu/webcam/sites/willowcreek/)


### Email

Want daily email updates of the Willow Creek Forecast? 

```{r}
textInput('email', "Email:")
actionButton('submit', "Submit", class = 'btn-primary')
```



```{r}
emails <- read.csv('/fs/data3/kzarada/NEFI/Willow_Creek/emails.csv', header = TRUE, stringsAsFactors = FALSE)

saveData <- function(input){
 emails <- rbind(emails, input)
  write.csv(emails, '/fs/data3/kzarada/NEFI/Willow_Creek/emails.csv', row.names = FALSE)
}

resetForm <- function(session){
  updateTextInput(session, "email", value = "Your Email has been added!")
}

observeEvent(input$submit, {
saveData(input$email)
resetForm(session)
})


```

Model Performance 
=======================================================================

Inputs {.sidebar}
-----------------------------------------------------------------------

```{r}
selectInput("var", "MET Variable:", 
            choices = c("Air Temp" = 'Tair', "Relative Humidity" = 'rH', 
                        "Soil Temp" = "Tsoil"), multiple = TRUE)

selectInput(inputId = "fdate", label="Forecast Horizon Date:", choices = c(rev(ctime[5:10])))
```

Row
-----------------------------------------------------------------------
###Regression Tree of Error 

```{r}

renderPlot({
  
  index <- which(names(nee.met) %in% input$var)
  
  
 if(length(index) >= 1){
  tree.df <- nee.met[,c(index, 13)]
  mod <- rpart(error ~ ., data = tree.df, method = 'anova')
  fancyRpartPlot(mod, sub = "")}

})

```

### Forecast Horizon
```{r}
renderPlot({
date <- lubridate::force_tz(as.POSIXct(paste(input$fdate, "12", sep = " "), format = "%Y-%m-%d %H"), "UTC")
sub.nee <- nee.data[which(nee.data$Time == date),] 

x.breaks = sub.nee$start_date
labels = rev(seq(from = 1, to = length(x.breaks), by = 1))


ggplot(sub.nee, aes(group = 1)) + 
  geom_ribbon(aes(x = start_date, ymin = Lower, ymax = Upper, fill="95% Confidence Interval"), alpha = 0.4) + 
  geom_line(aes(x = start_date, y = Predicted, color = "Predicted")) + 
  geom_line(aes(x = start_date, y = NEE, color = "Observed Data"), size = 1) +  
  ggtitle(paste0("Forecast Horizon for ", input$fdate)) +
  scale_color_manual(name = "Legend", labels = c("Observed Data", "Predicted"), values=c("Observed Data" = "firebrick4", "Predicted" = "skyblue1")) +
  scale_fill_manual(labels = c("95% Confidence Interval"), values=c("95% Confidence Interval" = "blue1")) +
  scale_y_continuous(name="NEE (kg C m-2 s-1)") + 
  scale_x_discrete(name = "Days from Observed Date", breaks = x.breaks, labels = labels) + 
  theme_minimal() + 
  theme(plot.title = element_text(hjust = 0.5, size = 12), legend.title = element_blank(), legend.text = element_text(size = 10), axis.text.x = element_text(size = 10), axis.text.y = element_text(size = 11), axis.title.y = element_text(size = 12)) 

})
```




Model by Start Date
=======================================================================

Inputs {.sidebar}
-----------------------------------------------------------------------

```{r}
selectInput(inputId = "date", label="Forecast Date:", choices = c(ctime[-c((length(ctime)-1),length(ctime))]))

```

Row
-----------------------------------------------------------------------

### Predictions vs Observed Data Time Series for NEE 

```{r}

renderPlot({
  
sub.nee <- nee.data[which(as.character(nee.data$start_date) == input$date),]
sub.nee <- sub.nee %>% filter(date < Sys.Date()) #%>% mutate(Time = as.factor(Time))

ggplot(sub.nee, aes(group = 1)) +
  geom_ribbon(aes(x = Time, ymin=Lower, ymax=Upper, fill="95% Confidence Interval"), alpha = 0.4)  + 
  geom_line(aes(x = Time, y = Predicted, color = "Predicted"), size = 1) +
  geom_line(aes(x = Time, y = NEE, color = "Observed")) + 
  ggtitle(paste0("NEE from ", input$date, " forecast")) +
  scale_color_manual(labels = c("Observed", "Predicted"), values=c("Observed" = "firebrick4", "Predicted" = "skyblue1")) +
  scale_fill_manual(labels = c("95% Confidence Interval"), values=c("95% Confidence Interval" = "blue1")) + 
  scale_y_continuous(name="NEE (kg C m-2 s-1)") + 
  #scale_x_discrete(name = "Time", breaks = x.breaks, labels = format(x.breaks, "%m-%d")) + 
  theme_minimal() + 
  theme(plot.title = element_text(hjust = 0.5, size = 16), legend.title = element_blank(), legend.text = element_text(size = 12), axis.text.x = element_text(size = 10), axis.text.y = element_text(size = 13), axis.title.y = element_text(size = 16)) 

})  

```


### Predictions vs Observed Scatter for NEE

```{r}

renderPlot({
  
    #subset data by start date    
  sub.nee <- subset(nee.data, nee.data$start_date == input$date)
  sub.nee <- sub.nee %>% filter(date < Sys.Date()) %>% mutate(Time = as.factor(Time))

E = sub.nee$Predicted
O = sub.nee$NEE
all = c(E, O)
RMSE = sqrt(mean((E-O)^2, na.rm = T))
Bias = mean(E-O, na.rm = T)

#Predicted vs Observed Scatter + 1:1 line + regression
par(pty="s") 
plot(E, O, pch = 19, cex = 0.7,  ylab = "Observed", xlab = "Predicted", 
     xlim = c(min(all, na.rm = T), max(all, na.rm = T)), 
     ylim = c(min(all, na.rm = T), max(all, na.rm = T)),
     main = paste0(unique(sub.nee$start_date), " forecast"), asp = 1)
abline(0,1, col = 'darkgrey', lwd = 3)
#abline(NEE.fit, col = "lightgrey", lwd = 2, lty = 2)
legend("bottomleft",legend=c('obs','1:1'),col= c('black', "darkgrey"),lwd=3, cex = 0.8)
mtext(text = paste0("RMSE = ", formatC(RMSE, format = "e", digits = 2)), 
      side = 3, line = 0, adj = -0.01, cex = 0.8) 

    
  })

```

### NEE Error by days from forecast day to observed day

```{r}
renderPlot({
sub.nee <- nee.data[which(as.character(nee.data$start_date) == input$date),]
sub.nee <- sub.nee %>% filter(date < Sys.Date()) %>% mutate(Time = as.factor(Time))
sub.nee$Hour <- as.factor(lubridate::hour(sub.nee$Time))
sub.nee$Time = lubridate::force_tz(as.POSIXct(sub.nee$Time), tz = "UTC")


ggplot(sub.nee, aes(x = Time, y = error, group = 1)) + 
  geom_point(aes(color = Hour), size = 3) + 
  geom_hline(yintercept = 0, color = "black") + 
  xlab("Date") + 
  scale_y_continuous(name = "NEE Error (kg C m-2 s-1)") + 
  theme_minimal() + 
  theme(axis.title.x = element_text(size = 14), axis.text.x = element_text(size = 12), axis.text.y = element_text(size = 12), axis.title.y = element_text(size = 14), legend.title = element_text(size = 14), legend.text = element_text(size = 12))

  
})  

```


### Predictions vs Observed Data Time Series for LE 

```{r}

renderPlot({
  
 sub.le <- le.data[which(as.character(le.data$start_date) == input$date),]
sub.le <- sub.le %>% filter(date < Sys.Date()) #%>% mutate(Time = as.factor(Time))

ggplot(sub.le, aes(group = 1)) +
  geom_ribbon(aes(x = Time, ymin=Lower, ymax=Upper, fill="95% Confidence Interval"), alpha = 0.4)  + 
  geom_line(aes(x = Time, y = Predicted, color = "Predicted"), size = 1) +
  geom_line(aes(x = Time, y = LE, color = "Observed")) + 
  ggtitle(paste0("LE from ", input$date, " forecast")) +
  scale_color_manual(labels = c("Observed", "Predicted"), values=c("Observed" = "firebrick4", "Predicted" = "skyblue1")) +
  scale_fill_manual(labels = c("95% Confidence Interval"), values=c("95% Confidence Interval" = "blue1")) + 
  scale_y_continuous(name="LE (W m-2 s-1)") + 
  #scale_x_discrete(name = "Time", breaks = x.breaks, labels = format(lab[-length(lab)], "%m-%d")) + 
  theme_minimal() + 
  theme(plot.title = element_text(hjust = 0.5, size = 16), legend.title = element_blank(), legend.text = element_text(size = 12), axis.text.x = element_text(size = 12), axis.text.y = element_text(size = 13), axis.title.y = element_text(size = 16)) 

})  

```



### Predictions vs Observed Scatter for LE

```{r}

renderPlot({
  
#subset data by start date    
sub.le <- le.data[which(as.character(le.data$start_date) == input$date),]
sub.le <- sub.le %>% filter(date < Sys.Date()) %>% mutate(Time = as.factor(Time))
sub.le$Hour <- as.factor(lubridate::hour(sub.le$Time))
sub.le$Time = lubridate::force_tz(as.POSIXct(sub.le$Time), tz = "UTC")


E = sub.le$Predicted
O = sub.le$LE
all = c(E, O)
RMSE = sqrt(mean((E-O)^2, na.rm = T))
Bias = mean(E-O, na.rm = T)

#Predicted vs Observed Scatter + 1:1 line + regression
par(pty="s") 
plot(E, O, pch = 19, cex = 0.7,  ylab = "Observed", xlab = "Predicted", 
     xlim = c(min(all, na.rm = T),30), 
     ylim = c(min(all, na.rm = T), 30),
     main = paste0(unique(sub.le$start_date), " forecast"), asp = 1)
abline(0,1, col = 'darkgrey', lwd = 3)
#abline(NEE.fit, col = "lightgrey", lwd = 2, lty = 2)
legend("topright",legend=c('obs','1:1'),col= c('black', "darkgrey"),lwd=3, cex = 0.8)
mtext(text = paste0("RMSE = ", formatC(RMSE, format = "e", digits = 2)), 
      side = 3, line = 0, adj = -0.01, cex = 0.8) 

  })

```

### LE Error by days from forecast day to observed day

```{r}
renderPlot({
sub.le <- le.data[which(as.character(le.data$start_date) == input$date),]
sub.le <- sub.le %>% filter(date < Sys.Date()) %>% mutate(Time = as.factor(Time))
sub.le$Hour <- as.factor(lubridate::hour(sub.le$Time))
sub.le$Time = lubridate::force_tz(as.POSIXct(sub.le$Time), tz = "UTC")

ggplot(sub.le, aes(x = Time, y = error, group = 1)) + 
  geom_point(aes(color = Hour), size = 3) + 
  geom_hline(yintercept = 0, color = "black") + 
  xlab("Date") + 
  scale_y_continuous(name = "LE Error (kg C m-2 s-1)") + 
  theme_minimal() + 
  theme(axis.title.x = element_text(size = 14), axis.text.x = element_text(size = 12), axis.text.y = element_text(size = 12), axis.title.y = element_text(size = 14), legend.title = element_text(size = 14), legend.text = element_text(size = 12))


  
})  

```

### Predictions vs Observed Data Time Series for Soil Moisture Fraction 
```{r}
renderPlot({
  
 sub.soil <- soil.data[which(as.character(soil.data$start_date) == input$date),]
 sub.soil <- sub.soil %>% filter(date < Sys.Date()) #%>% mutate(Time = as.factor(Time))

ggplot(sub.soil, aes(group = 1)) +
  geom_ribbon(aes(x = Time, ymin=Lower, ymax=Upper, fill="95% Confidence Interval"), alpha = 0.4)  + 
  geom_line(aes(x = Time, y = Predicted, color = "Predicted"), size = 1) +
  geom_line(aes(x = Time, y = avgsoil, color = "Observed")) + 
  ggtitle(paste0("Soil Moisture Fraction from ", input$date, " forecast")) +
  scale_color_manual(labels = c("Observed", "Predicted"), values=c("Observed" = "firebrick4", "Predicted" = "skyblue1")) +
  scale_fill_manual(labels = c("95% Confidence Interval"), values=c("95% Confidence Interval" = "blue1")) + 
  scale_y_continuous(name="Soilt Moisture (%)") + 
  #scale_x_discrete(name = "Time", breaks = x.breaks, labels = format(lab[-length(lab)], "%m-%d")) + 
  theme_minimal() + 
  theme(plot.title = element_text(hjust = 0.5, size = 16), legend.title = element_blank(), legend.text = element_text(size = 12), axis.text.x = element_text(size = 12), axis.text.y = element_text(size = 13), axis.title.y = element_text(size = 16)) 

})  

```

### Predictions vs Observed Scatter for Soil Moisture

```{r}
renderPlot({
  
#subset data by start date    
sub.soil <- soil.data[which(as.character(soil.data$start_date) == input$date),]
sub.soil <- sub.soil %>% filter(date < Sys.Date()) %>% mutate(Time = as.factor(Time))
sub.soil$Hour <- as.factor(lubridate::hour(sub.soil$Time))
sub.soil$Time = lubridate::force_tz(as.POSIXct(sub.soil$Time), tz = "UTC")


E = sub.soil$Predicted
O = sub.soil$avgsoil
all = c(E, O)
RMSE = sqrt(mean((E-O)^2, na.rm = T))
Bias = mean(E-O, na.rm = T)

#Predicted vs Observed Scatter + 1:1 line + regression
par(pty="s") 
plot(E, O, pch = 19, cex = 0.7,  ylab = "Observed", xlab = "Predicted", 
     xlim = c(min(all, na.rm = T),1), 
     ylim = c(min(all, na.rm = T), 1),
     main = paste0(unique(sub.soil$start_date), " forecast"), asp = 1)
abline(0,1, col = 'darkgrey', lwd = 3)
#abline(NEE.fit, col = "lightgrey", lwd = 2, lty = 2)
legend("topright",legend=c('obs','1:1'),col= c('black', "darkgrey"),lwd=3, cex = 0.8)
mtext(text = paste0("RMSE = ", formatC(RMSE, format = "e", digits = 2)), 
      side = 3, line = 0, adj = -0.01, cex = 0.8) 

  })


```

### Soil Moisture Fraction Error by days from forecast day to observed day

```{r}
renderPlot({
sub.soil <- soil.data[which(as.character(soil.data$start_date) == input$date),]
sub.soil <- sub.soil %>% filter(date < Sys.Date()) %>% mutate(Time = as.factor(Time))
sub.soil$Hour <- as.factor(lubridate::hour(sub.soil$Time))
sub.soil$Time = lubridate::force_tz(as.POSIXct(sub.soil$Time), tz = "UTC")

ggplot(sub.soil, aes(x = Time, y = error, group = 1)) + 
  geom_point(aes(color = Hour), size = 3) + 
  geom_hline(yintercept = 0, color = "black") + 
  xlab("Date") + 
  scale_y_continuous(name = "Soil Moisture Error") + 
  theme_minimal() + 
  theme(axis.title.x = element_text(size = 14), axis.text.x = element_text(size = 12), axis.text.y = element_text(size = 12), axis.title.y = element_text(size = 14), legend.title = element_text(size = 14), legend.text = element_text(size = 12))


  
})  

```




NOAA GEFS
=======================================================================
  
The WCr Carbon Flux forecast uses the 16 day NOAA GEFS meterological ensemble forecast. Explore the meterological data below: 
  
### Air Temperature (Celsius)
```{r}
ggplotly(ggplot(forecasted_data, aes(y = Tair_C, x = timestamp, group = ensemble)) + 
    geom_line(aes(y = Tair_C, x = timestamp, color = ensemble))+ 
    theme(legend.position = 'none') + 
    ggtitle(paste0("GEFS Air Temp Forecast from ", Sys.Date())))
```

### Specific Humidity
```{r}
ggplotly(ggplot(forecasted_data, aes(y = Qair, x = timestamp, group = ensemble)) + 
  geom_line(aes(y = Qair, x = timestamp, color = ensemble))+ 
  theme(legend.position = 'none') + 
  ggtitle(paste0("GEFS Specific Humidity Forecast from ", Sys.Date())))
```

### Rain
```{r}
ggplotly(ggplot(forecasted_data, aes(y = Rain, x = timestamp, group = ensemble)) + 
  geom_line(aes(y = Rain, x = timestamp, color = ensemble))+ 
  theme(legend.position = 'none') + 
  ggtitle(paste0("GEFS Rain Forecast from ", Sys.Date())))

```

### Wind Speed
```{r}
ggplotly(ggplot(forecasted_data, aes(y = ws, x = timestamp, group = ensemble)) + 
  geom_line(aes(y = ws, x = timestamp, color = ensemble))+ 
  theme(legend.position = 'none') + 
  ggtitle(paste0("GEFS Wind Speed Forecast from ", Sys.Date())))

```

### Shortwave Radiation
```{r}
ggplotly(ggplot(forecasted_data, aes(y = SW, x = timestamp, group = ensemble)) + 
  geom_line(aes(y = SW, x = timestamp, color = ensemble))+ 
  theme(legend.position = 'none') + 
  ggtitle(paste0("GEFS Shortwave Radiation Forecast from ", Sys.Date())))
```


### Longwave Radiation
```{r}
ggplotly(ggplot(forecasted_data, aes(y = LW, x = timestamp, group = ensemble)) + 
  geom_line(aes(y = LW, x = timestamp, color = ensemble))+ 
  theme(legend.position = 'none') + 
  ggtitle(paste0("GEFS Longwave Radiation Forecast from ", Sys.Date()))
)
```

Data Download
=======================================================================
  
Download Forecast data: 
  
```{r, echo = FALSE}
shiny::HTML('<iframe src = "/output/" width = "100%" height = "800" frameborder=0>
         Sorry your browser does not support inline frames.
      </iframe>')

```

